References for PloS paper

### 2014-02-17 image_analysis_paper/background_reading/article_notes.tex
added more notes for literature

\item \fullcite{wei2006conditional}

\item \fullcite{wei2006quantile}

>>>>

\item \fullcite{wei2006conditional}
\begin{itemize}
		\item Want to develop a more informative growth chart metric
		\item Instead of looking at how atypical a current measurement is for an individual, they look at how atypical a time series is for an individual 
		\item This means that a person will be flagged if, for example, their weight changes dramatically in a short period of time, even if both measurements are within the ``normal'' range
		\item Fit model to data for ``normal'' time--series behavior
\end{itemize}

\item \fullcite{wei2006quantile}
\begin{itemize}
	\item Develop nonparameteric models (using spline regression) for growth charts
	\item Typical growth charts rely on normality assumptions (data is often transformed to fulfill such assumptions)
	\item Using nonparametric models can allow them to fit a much broader range of behaviors (i.e. bimodal distributions)
\end{itemize}
